Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-02-19 paper/ms.tex
allow bounds dict with named parameters
implementing a kernel product

% Copyright 2015-2016 Dan Foreman-Mackey and the co-authors listed below.

@@

\begin{enumerate}
\item an OU process
\item a full celerite process
\item some sort of QP oscillation
\end{enumerate}

>>>>

% Copyright 2015-2017 Dan Foreman-Mackey and the co-authors listed below.

@@

\subsection{Recovery of a celerite process}

In this first example, we will simulate a dataset using a known \celerite\
process and fit it with \celerite\ to demonstrate that valid inferences can be
made in this idealized case.

\subsection{Inferences with the ``wrong'' model}

For this example, we will simulate two datasets using known GP models with
kernels outside of the support of a \celerite\ process.
We will use these simulations to demonstrate that, at least in these cases,
valid inferences can be made about the physical parameters of the model even
if the effective covariance function is known to be ``wrong''.
